%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Thomas J. Brailey}{}

\position{MPhil in Politics}
\address{Oxford, United Kingdom}

\email{\href{mailto:thomasjbrailey@gmail.com}{\nolinkurl{thomasjbrailey@gmail.com}}}
\github{tjbrailey}
\linkedin{tjbrailey}
\twitter{tjbrailey}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {April, 2024}
    {Thomas J. Brailey~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{MPhil, Comparative Government}{University of Oxford}{Oxford, United Kingdom}{2022-2024}{}\vspace{-4.0mm}
    \cventry{Bachelor of Science, Political Science/Data Analytics}{University of California, San Diego}{San Diego, United States}{2016-2020}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{research-experience}{%
\section{Research Experience}\label{research-experience}}

\begin{cventries}
    \cventry{Research Assistant}{University of Oxford}{Oxford, United Kingdom}{2022-Present}{\begin{cvitems}
\item Co-authoring research with the Departments of Sociology and of Politics and International Relations.
\item Conducting data cleaning, exploratory data analysis, and testing theoretical mechanisms with data.
\item Transferring codebases to version-controlled GitHub setup.
\end{cvitems}}
    \cventry{Pre-Doctoral Fellow}{Payments and Governance Research Program}{San Diego, United States}{2020-2022}{\begin{cvitems}
\item Conducted exploratory data analysis and data visualization across several research projects.
\item Coordinated the transition of all code to GitHub and introducing RAs/GSRs to version control.
\item Edited manuscripts and preparing presentations for government leaders and other stakeholders.
\end{cvitems}}
    \cventry{Research Assistant}{Center for the Study of African Political Economy}{San Diego, United States}{2018-2020}{\begin{cvitems}
\item Independently developed a large-N database of election statistics across all recognized states.
\item Used R to combine and reshape multiple datasets, visualize the data, and perform statistical analysis.
\item Manually inputted missing data from newspapers and reports to ensure completeness of data.
\end{cvitems}}
    \cventry{Research/Lab Assistant}{Center for Peace and Security Studies}{San Diego, United States}{2018-2020}{\begin{cvitems}
\item Used R to conduct quantitative analyses on large-N datasets.
\item Generated graphs, tables, and figures in R and LaTeX for research papers and conference presentations.
\item Wrote briefs on my data analysis and code and presented findings.
\end{cvitems}}
\end{cventries}

\hypertarget{publications-as-author}{%
\subsection{Publications-As Author}\label{publications-as-author}}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-Brodeur2024}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Brodeur, A., Mikola, D., Cook, N., Brailey, T., Briggs,
R., De Gendre, A., Dupraz, Y., Fiala, L., Gabani, J., Gauriot, R.,
Haddad, J., Lima, G., Ankel-Peters, J., \& Dreber, A. (2024). \emph{Mass
Reproducibility and Replicability: A New Hope}.}

\leavevmode\vadjust pre{\hypertarget{ref-Brailey2023}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Brailey, T., Hepplewhite, M., \& Moser, S. (2023).
\emph{Direct Replication and Additional Sensitivity and Robustness
Analyses for Frederiksen (2022): A Replication Report from the
Nottingham Replication Games}.
\url{https://doi.org/10.2139/ssrn.4437368}}

\hypertarget{publications-as-research-assistant}{%
\subsection{Publications-As Research
Assistant}\label{publications-as-research-assistant}}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-Gannon2024}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Gannon, J. A., Gartzke, E., Lindsay, J. R., \& Schram,
P. (2024). The Shadow of Deterrence: Why Capable Actors Engage in
Contests Short of War. \emph{Journal of Conflict Resolution},
\emph{68}(2-3), 230--268.
\url{https://doi.org/10.1177/00220027231166345}}

\leavevmode\vadjust pre{\hypertarget{ref-Gannon2023}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Gannon, J. A. (2023). Planes, Trains, and Armored
Mobiles: Introducing a Dataset of the Global Distribution of Military
Capabilities. \emph{International Studies Quarterly}, \emph{67}(4).
\url{https://doi.org/10.1093/isq/sqad081}}

\leavevmode\vadjust pre{\hypertarget{ref-Muralidharan2023}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Muralidharan, K., Niehaus, P., \& Sukhtankar, S. (2023).
General Equilibrium Effects of (Improving) Public Employment Programs:
Experimental Evidence From India. \emph{Econometrica}, \emph{91}(4),
1261--1295. \url{https://doi.org/10.3982/ecta18181}}

\leavevmode\vadjust pre{\hypertarget{ref-Faridani2022}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Faridani, S., \& Niehaus, P. (2022). \emph{Rate-optimal
linear estimation of average global effects}.
\url{https://arxiv.org/abs/2209.14181v2}}

\leavevmode\vadjust pre{\hypertarget{ref-Gannon2022}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{Gannon, J. A. (2022). One if by Land, and Two if by Sea:
Cross-Domain Contests and the Escalation of International Crises.
\emph{International Studies Quarterly}, \emph{66}(4), 474--475.
\url{https://doi.org/10.1093/isq/sqac065}}

\leavevmode\vadjust pre{\hypertarget{ref-Gaikwad2021}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{Gaikwad, N., \& Nellis, G. (2021). Overcoming the
Political Exclusion of Migrants: Theory and Experimental Evidence from
India. \emph{American Political Science Review}, \emph{115}, 1--18.
\url{https://doi.org/10.1017/S0003055421000435}}

\leavevmode\vadjust pre{\hypertarget{ref-Muralidharan2020}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{Muralidharan, K., Niehaus, P., \& Sukhtankar, S. (2021).
\emph{Identity Verification Standards in Welfare Programs: Experimental
Evidence from India}.
\url{https://www.socialscienceregistry.org/trials/1620}}

\hypertarget{conference-invites}{%
\section{Conference Invites}\label{conference-invites}}

\begin{cvhonors}
    \cvhonor{}{Midwestern Political Science Association}{Chicago}{2024}
    \cvhonor{}{Political Science Association}{Virtual}{2023}
    \cvhonor{}{American Political Science Association}{Virtual}{2021}
    \cvhonor{}{International Studies Association}{Virtual}{2021}
    \cvhonor{}{Midwestern Political Science Association}{Chicago, cancelled}{2020}
    \cvhonor{}{International Studies Association}{Honolulu, cancelled}{2020}
    \cvhonor{}{Souther California Research Conference}{San Diego}{2019}
    \cvhonor{}{Western Political Science Association}{San Diego}{2019}
\end{cvhonors}

\hypertarget{scholarship-and-awards}{%
\section{Scholarship and Awards}\label{scholarship-and-awards}}

\begin{cvhonors}
    \cvhonor{}{Cyril Foster Award}{University of Oxford}{2024}
    \cvhonor{}{Research Grant}{University of Oxford}{2023}
    \cvhonor{}{Clarendon Scholarship}{University of Oxford}{2022-2024}
    \cvhonor{}{Catalyst Grant}{Berkeley Institute for Transparency in the Social Sciences}{2021}
    \cvhonor{}{Sanford Lakoff Award for the Most Outstanding Thesis}{UC San Diego}{2020}
    \cvhonor{}{Pi Sigma Alpha}{UC San Diego}{2017-2020}
    \cvhonor{}{Provost Honors}{UC San Diego}{2016-2020}
    \cvhonor{}{Outstanding Resident}{UC San Diego}{2017}
\end{cvhonors}

\hypertarget{volunteer-experience}{%
\section{Volunteer Experience}\label{volunteer-experience}}

\begin{cvhonors}
    \cvhonor{}{Volunteer data scientist for DataKind UK}{}{}
    \cvhonor{}{Co-found of the Political Science Student Association at UCSD}{}{}
    \cvhonor{}{Employment Assistant at the International Rescue Committee}{}{}
    \cvhonor{}{Tutor for San Diego's Refugee Tutoring Program}{}{}
\end{cvhonors}

\hypertarget{training-and-skills}{%
\section{Training and Skills}\label{training-and-skills}}

\hypertarget{training}{%
\subsection{Training}\label{training}}

\begin{cvhonors}
    \cvhonor{}{Oxford Spring School for Advanced Research Methods (Qualitative Methods, 2024)}{}{}
    \cvhonor{}{European Consortium for Political Research (Bayesian Statistics, 2023)}{}{}
    \cvhonor{}{Oxford Spring School for Advanced Research Methods (Machine Learning, 2023)}{}{}
\end{cvhonors}

\hypertarget{skills}{%
\subsection{Skills}\label{skills}}

\hypertarget{spoken-languages}{%
\subsubsection{Spoken Languages}\label{spoken-languages}}

\begin{cvhonors}
    \cvhonor{}{English (Native), French (Beginner), Arabic (Beginner)}{}{}
\end{cvhonors}

\hypertarget{technical-languages}{%
\subsubsection{Technical Languages}\label{technical-languages}}

\begin{cvhonors}
    \cvhonor{}{Proficient: ArcGIS, Git, Latex, R, SPSS, STATA}{}{}
    \cvhonor{}{Beginner: Python, SQL, Tableau, Stan, Julia}{}{}
\end{cvhonors}

\hypertarget{softwares}{%
\subsubsection{Softwares}\label{softwares}}

\begin{cvhonors}
    \cvhonor{}{Amazon Web Services, Microsoft Office}{}{}
\end{cvhonors}



\end{document}
